---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jsquiz

<!-- badges: start -->
<!-- badges: end -->

`{jsquiz}` generates quizzes in a form of multiple-choice questions. The business logic is implemented using JavaScript, therefore, no back-end required (e.g., Shiny). This package was developed to allow for exercises in `{bookdown}` books. Currently, works only with `{bookdown}` projects, but with a slight modification, one can include those exercises into regular R Markdown and Quatro documents.

**Note:** Please treat this package just as a proof of concept! 

## Installation

You can install the development version of `{jsquiz}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("irudnyts/jsquiz")
```

## Example

To use the package, one needs to initialize it first by `initialize()` function. This function will add all necessary CSS and JavaScript files. This function is supposed to be run from the console **only one time**:

```{r, eval=FALSE}
initialize()
```

Then, quizzes can be added by using function `generate_mcq()` in a separate code chunks. This function will generate HTML tags for multiple-choice questions:

````markdown
`r ''````{r, results='asis', message=FALSE, echo=FALSE}
library(jsquiz)
jsquiz::generate_mcq()
```
````

If you want to generate multiple-choice question and allow for multiple options, you can set `allow_multiple_answers = TRUE`. In the following example, we set all argument values to non-default values: 

````markdown
`r ''````{r, results='asis', message=FALSE, echo=FALSE}
jsquiz::generate_mcq(
    question = "Select programming langauges:",
    answers = c(
        "Python" = TRUE,
        "C++" = TRUE,
        "RStudio" = FALSE
    ),
    button_label = "Submit",
    allow_multiple_answers = TRUE
)
```
````

Please do not forget to load `{jsquiz}` somewhere and mind the following values of chunk's options: 

* `results='asis'`
* `message=FALSE`
* `echo=FALSE`

