---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jsquiz

<!-- badges: start -->
<!-- badges: end -->

`{jsquiz}` generates quizzes in a form of multiple-choice questions. The business logic is implemented using JavaScript, therefore, no back-end required (e.g., Shiny). This package was developed to allow for exercises in `{bookdown}` books. Currently, works only with `{bookdown}` projects, but with a slight modification, one can include those exercises into regular R Markdown and Quatro documents.

**Note:** Please treat this package just as a proof of concept! 

## Installation

You can install the development version of `{jsquiz}` from [GitHub](https://github.com/) with:

``` r
devtools::install_github("irudnyts/jsquiz")
```

## Example

To use the package, one needs to initialize it first by `init()` function. This function will add all necessary CSS and JavaScript files. This function is supposed to be run from the console **only one time**:

```{r, eval=FALSE}
init()
```

## Multiple choice question (options quiz): `generate_options_quiz()`

Then, MCQ quizzes can be added by using function `generate_options_quiz()` in a separate code chunks. This function will generate HTML tags for multiple-choice questions:

````markdown
`r ''````{r, results='asis', message=FALSE, echo=FALSE}
jsquiz::generate_options_quiz()
```
````

If you want to generate multiple-choice question and allow for multiple options, you can set `allow_multiple_answers = TRUE`. In the following example, we set all argument values to non-default values: 

````markdown
`r ''````{r, results='asis', message=FALSE, echo=FALSE}
jsquiz::generate_options_quiz(
    question = "Select programming langauges:",
    answers = c(
        "Python" = TRUE,
        "C++" = TRUE,
        "RStudio" = FALSE
    ),
    button_label = "Submit",
    allow_multiple_answers = TRUE
)
```
````

It is recommended to load `{jsquiz}` somewhere (and to stop using namespace prefix `jsquiz::`). Further, please mind the following values of chunk's options: 

* `results='asis'`
* `message=FALSE`
* `echo=FALSE`

## Arrange quiz: `generate_arrange_quiz()`

````markdown
`r ''````{r, results='asis', message=FALSE, echo=FALSE}
jsquiz::generate_arrange_quiz()
```
````

## Setting custom success/failure messages and submit button label 

One can set global (for the entire `{bookdown}` document) custom success/failure messages and submit button label. Please use `set_success_messages()`, `set_failure_messages()`, and `set_button_label()` for this purpose somewhere in at the begining of your book: 

```{r, eval = FALSE}
jsquiz::set_button_label("Submit")

jsquiz::set_success_messages(c("Good job!", "Bravo!"))

jsquiz::set_failure_messages(c("Oops!", "Try again!"))
```

This feature can be used, if your book in other than English language.

Further, it is also possible to set success/failure messages and submit button label individually for each question. It cover very specific cases and generaly makes very little sense.

